\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-05 paper.tex
15. Explicitly state moderation of interests. Most of conclusion changed/rewritten.

The interests of the software engineer, creating content that players love, and the interests of the player are complimentary. Players are interested in great content and a full-featured experience and Blizzard's engineers are interested in creating that exact experience and content.
Blizzard Entertainment's interests of growing as a company and keeping its shareholders satisfied are only improved by happy players. Happy players will recommend Blizzard and its products to friends as well as continue to pay monthly fees for World of Warcraft and buy Blizzards other games.

Having a majority of players who are \emph{not} addicted, and thus playing for pleasure or other purposes, is in line with the Utilitarian view of ethical and therefore in line with a cold, calculated numerical view of ``public good.''

Not only are a majority of users not addicted, many of these users are cultivating life skills, strong friendships, and powerful emotional experiences. These users are growing as individuals and going out into the world as stronger people with leadership and teamwork skills.
Some users are even overcoming physical and mental disabilities through use of the game. These users would be mentally and physically distraught without World of Warcraft and thus the public good would be diminished. Because the game is helping these users from having poor welfare, World of Warcraft, and other MMORPGs, can be seen as \emph{improving} the public good.

>>>>

Players are interested in achievement, social interactions, and immersion. Blizzard's engineers are interested in creating those exact experiences and content. The interests of the software engineer, creating content that players love, and the interests of the player are complimentary. In this way, the engineers are moderating their interests with the players.

Blizzard Entertainment's interests of growing as a company and keeping its shareholders satisfied are only improved by happy players. Happy players will recommend Blizzard and its products to friends as well as continue to pay monthly fees for World of Warcraft and buy Blizzard's other games. This is how Blizzard's and the player's interests are moderated.

Having a majority of players who are \emph{not} addicted, and thus playing for pleasure or other purposes, is in line with the Utilitarian view of ethical as World of Warcraft is not promoting mental disease and therefore in line with a cold, calculated numerical view of ``public good.''

Not only are a majority of users not addicted, over 50\% of these users are cultivating life skills, strong friendships, and powerful emotional experiences. \cite{MotivationsAndDerviedExperiences} These users are growing as individuals and going out into the world as stronger people with leadership and teamwork skills. Because the game is improving users, World of Warcraft, and other MMORPGs, can be seen as \emph{improving} the public good. By improving the public good, Blizzard's engineers are moderating the interests of all parties with the public good.
